---
title: "Julie learning Python"
author: "Julie Lowndes"
date: "6/12/2020"
output: html_document
---

## Summary

I want to learn Python from RStudio, since I already use RStudio as a workflow with R and GitHub. I know it is possible to run Python from RStudio and RMarkdown and I am trying this for myself here. 

Reviewed 2021-05-14 when brought into this repo: <https://github.com/jules32/learning-python>

## Setup

First, I had to download and install: 

1. Python: <https://www.python.org/downloads/>
1. Anaconda: <https://www.anaconda.com/products/individual#macos>

Then I could do the following in R:

https://rstudio.github.io/reticulate/.

```{r setup, message=FALSE}
## load R libraries
library(reticulate) #install.packages("reticulate")

## check reticulate and python
use_python("/usr/local/bin/python")
Sys.which("python") # "/usr/bin/python" just checking

## set up a python environment: create new environment (https://rstudio.github.io/reticulate/articles/python_packages.html)
# create a new environment 
conda_create("r-reticulate")

# install pandas
conda_install("r-reticulate", "pandas")

```


## Python Recipe

Walk through [
Python Recipe: Open a file, read it, print matching lines](https://palewi.re/posts/2008/04/05/python-recipe-open-a-file-read-through-it-print-each-line-matching-a-search-term/)

However! This is from 2008 so I expect a few things to be outdated. Particularly since there will likely be something with Python 3 vs 2. 

Step 1-2:
New link: http://www.gutenberg.org/cache/epub/1041/pg1041.txt

I downloaded this by hand after `curl` did not capture the text.

Skip step 3

Step 4: 

Will need to do something about filepath. Here I've changed the working directory in R. 

```{r, eval=FALSE}
dir.create('py-search')
setwd('py-search')
```

Copy-paste in a Python chunk:

Note: to run it you can't do command-enter because it will quit Python and go back to R.

Also note: the `print()` function was hanging, and I looked on Stack Overflow: 
https://stackoverflow.com/questions/6159900/correct-way-to-write-line-to-file

```{python}
#!/usr/bin/env python

import re

shakes = open("pg1041.txt", "r")
love = open("love.txt", "w")

for line in shakes:
    if re.match("(.*)(L|l)ove(.*)", line):
        print(line)  
        love.write(line)
```

Hitting return will then get your cursor back and also print the line numbers. 

Try sourcing .py script from R

```{r}
source_python('love_test.py') 

# ggplot(r$love...)
```


## Quick Intro Pandas

Walk through this [quick intro to pandas](https://towardsdatascience.com/a-quick-introduction-to-the-pandas-python-library-f1b678f34673), recommended by Oliver Tam.

Note: when I run this whole chunk, it asks to install a newer version of Miniconda (in the Console), png (as a dialogue that then executed in the Jobs tab), and a few other Pythony things. I said yes to each of them.

```{python, error=TRUE}
## importing libraries
import pandas as pd 
import numpy as np 

## reading in data. Functions have this structure: pd.read_filetype().
pd.read_csv("../gene_expression_from_table/expression_tables/gene_counts.csv")

## converting other Python objects (lists, dictionaries, etc) into dataframe: pd.DataFrame()

## saving your dataframe to output: df.to_filetype(filename)
## NOTE: since x is in the function call (x.to_csv), you don't need it as a variable
x = pd.read_csv("../gene_expression_from_table/expression_tables/gene_counts.csv")
x.to_csv("../gene_expression_from_table/jules32/testing_save_to_csv2.csv")


```

### Other practice from Allison: 
```{python}
# Create the function:
def subtract_this(arg1, arg2):
  solution = arg1 - arg2
  print(solution)
  
subtract_this(100, 2)

# Example 1: print a list with a for loop
dogs = ["teddy", "khora", "maggie"]
# Run a for loop to print them: 
for i in dogs: 
  print(i)
```

