---
title: "NASA Openscapes Carpentries1"
author: "Julie Lowndes"
date: "5/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro to Python May 2021


<https://virdi.github.io/2021-05-17-openscapes-online/>

<https://swcarpentry.github.io/shell-novice/setup.html>

<https://pad.carpentries.org/2021-05-17-openscapes-online>

[Bia's awesome slides](https://docs.google.com/presentation/d/1YEIvzHosnnrBkqvgDafal8JwGvjh9A7dsD5dQYg4DcY/edit#slide=id.g8954b9e7ca_7_53)

Bia's recommended juypter notbook cheatsheet: [Download from Edureka ](https://www.edureka.co/blog/wp-content/uploads/2018/10/Jupyter_Notebook_CheatSheet_Edureka.pdf)



## RStudio setup
```{r setup}
library(reticulate)
library(here)
setwd(here("nasa-openscapes/carpentries-python"))

```

```{python}
5*2
weight_kg = 60
print(weight_kg)
print('weight in pounds', 2.2 * weight_kg)

jedi1, jedi2 = 'Luke', 'Obi-Wan'
print(jedi1, jedi2)
print(jedi1)

first, second = 'computing',' cloud'
print(first, second)
thrid, fourth = second, first
print(thrid, fourth)
```


```{python}
project_name = 'open science'

new = project_name[5:12]
print(new)

```


```{python}
import numpy as np

## np.loadtxt # this is like "blender.crush_ice()

np.loadtxt(fname='data/inflammation-01.csv', delimiter=',')
np.loadtxt? # what does this function do?
np. # tab will complete to help you figure out what functions exit
dir(np) # will show every property that that object has


data = np.loadtxt(fname='data/inflammation-01.csv', delimiter=',')
data.dtype
print(data) # an array

# to get the 3rd row and 2nd column: 
data[2,1]

data[1:4, 5:10]

np.mean(data)

patient_0 = data[0, :] # slice the first row
patient_0.shape 
np.max(patient_0)

```

## install python module "matplotlib"
<https://swcarpentry.github.io/python-novice-inflammation/03-matplotlib/index.html>

```{r}
py_install("matplotlib")
```

No non-system installation of Python could be found.
Would you like to download and install Miniconda?
Miniconda is an open source environment management system for Python.
See https://docs.conda.io/en/latest/miniconda.html for more details.

Would you like to install Miniconda? [Y/n]: y


```{python}
import matplotlib.pyplot as plt # if error install above in R

image = plt.imshow(data)


ave_inflammation = np.mean(data, axis=0)
ave_plot = plt.plot(ave_inflammation)
plt.show()

```

```{python}
agency = "NASA"
print(agency[0])
print(agency[1])
print(agency[2])
print(agency[3])

jedi_name = 'Luke Skywalker'
i = 0
for char in jedi_name:
  print(i)
  i = i+1

```


```{python}
import glob
```


## GitHub notes

https://jcszamosi.github.io/mcmaster_swc_git/04-create/


https://rogerdudler.github.io/git-guide/

